---
title: "Aquaculture Model"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r pkg_ins, include = FALSE}

# Check out knitr for knitr::read_chunk.
library(knitr)

# Name packages.
pkg <- c("readr",
         "knitr",
         "tidyverse",
         "gapminder",
         "sandwich",
         "broom",
         "stargazer",
         "cowplot")

# Install packages.
#install.packages(pkg, verbose = FALSE, quiet = TRUE)

  
# Update packages.
#update.packages(pkg, verbose = FALSE, quiet = TRUE)

# Check out packages.
lapply(pkg, library, character.only = TRUE)

```

#####Objective: Step through optimal harvest and planting decisions by a generic totoaba farm..

Toy Model:

Parameters for White seabass (Cynoscion nobiliis) from:
Thomas, J. C. (1968). Management of the white seabass (Cynoscion nobilis) in California waters. State of California. The Resources Agency. Department of Fish and Game.

#####Von Bertalanffy Growth Model

$L(t) = L_\infty ( 1 - e^{ - K ( t - t_0 )})$

Variable   | Definition
---------- | ---------------------------
*L*        | Length (Millimeters)
$L_\infty$ | Maximum Length (mm)
*K*        | Catabolic Constant (?!)
*t*        | Age (Years)
$t_0$      | Age, *L* = 0

```{r al_function}

# Von Bertalanffy function.
fn_vb = function(linf, k, t, t_0){l = linf * ( 1 - exp( - k * ( t - t_0)))}

# White seabass demo with age in years and length in millimeters.
v_vb_a_wsb = seq(0, 25)
v_vb_l_wsb = fn_vb(1465.3822, 0.1280, v_vb_a_wsb, -0.2805)
plot(v_vb_a_wsb, v_vb_l_wsb)


# Totoaba demo.
#v_vb_a_tma = seq(a0, amax)
#v_vb_l_tma = fn_vb(linf, k, v_vb_a_tma, t_0)
#plot(v_vb_a_tma, v_vb_l_tma)

```

#####Weight-Length Conversion

$W = aL^b$

Variable   | Definition
---------- | ---------------------------
*W*        | Weight (Grams)
*a*        | Length (Millimeters)
*L*        | Parameter
*b*        | Parameter

```{r lw_function}

# Generic length-to-weight conversion. 
fn_lw = function(a, l, b){ w = a * l ^ b }

# White seabass demo in mm:g.
v_lw_l_wsb = seq(0, 1500, by = 100)
v_lw_w_wsb = fn_lw(0.000015491, v_lw_l_wsb, 2.92167)
plot(v_lw_l_wsb, v_lw_w_wsb)

# Totoaba demo.
#v_lw_l_tma = seq(l0, linf, by = 100)
#v_lw_w_tma = fn_lw(a, v_lw_l_tma, b)
#plot(v_lw_l_tma, v_lw_w_tma)

```

#####Weight-Maw Conversion

For a stock of $n_{a, t}$ totoaba cultivated for *a* years in year *t* to weight $w_{a, t}$ for a total round weight of $x_{a, t}$, maw yield $y_{a, t}$ depends on wet maw yield ratio $c^{maw}_{a, t}$ and dry yield ratio $k$.

$y^{maw}_{a, t} = w_{a, t}n_{a, t}c^{maw}_{a, t}k^{maw}_{dry}$

Variable   | Definition
---------- | --------------------------------
$y^{maw}$  | Cohort Dry Maw Yield (Kilograms)
*w*        | Individual Round Weight (Kilograms)
*n*        | Cohort Count
$c^{maw}$  | Yield of maw from round weight.
$k^{maw}$  | Yield of dry maw from wet maw.

```{r wm_function}

fn_wm = function(w, n, c, k){ymaw = w * n * c * k}

```

#####Maw-Price Conversion

Plug the market model in here. Use the following placeholder in the meantime.

```{r mp_function}

fn_mp = function(w, b0, bw, bq, q, bc, c){pmaw = b0 + w ^ bw + bq * q + bc * c}

```

#####Maw-Revenue Conversion

Fix from regression specification. See Maw-Price Conversion.

For a dry maw yield $y^{maw}$ in kilograms, revenue depends on price.

$R^{maw}_{a, t} = x_{a, t}/n_{a, t} * (\beta_0 + \beta_{g}(x_{a, t}/n_{a, t}))$

```{r mr_function}

fn_mr = function(y, pmaw){rmaw = ymaw * pmaw}

```


#####Weight-Fillet Conversion

For a stock of totoaba cultivated for *a* years in year *t* for a total round weight of $x_{a, t}$, fillet yield $y^{fil}_{a, t}$ depends on fillet yield ratio $c^{fil}_{a, t}$.

Variable | Definition
-------- | --------------------------------
$y^{fil}$| Cohort Fillet Yield (Kilograms)
*x*      | Cohort Round Weight (Kilograms)
$c^{fil}$| Fillet Yield Ratio (%)

```{r wf_function}

fn_wf = function(x, c){yfil = x * c}

```

#####Fillet-Revenue Conversion

For a fillet yield $y^{fil}$ in kilograms, revenue depends on price.

$R^{fil}_{a, t} = y^{fil}_{a, t} * p^{fil}$

```{r fp_function}

fn_fr = function(yfil, pfil){rfil = yfil * pfil}

```

#####Feed Conversion Function

Check in with Goto. Fix.

```{r fcr_function}

#fn_fcr = function(){}

```


#####No-Harvest Cost

Fix FCR, then fix this.

```{r c_stock}

# Feed costs for a cohort.

fn_ch0 = function(a, c){cstock = a ^ c}

```


#####Harvest Cost

Cost of restocking a cage after harvest. USD?

```{r c_restock}

# COst of fry plus overhead.

ch1 = 5000

```


#####Harvest Decision

help

```{r model}


q_aq = function(r, k, q, p, c, eta, x0, e0, start, end){
                     x = as.numeric(vector(length = (end - start)))
                     x[1] = x0
                     e = as.numeric(vector(length = (end - start)))
                     e[1] = e0
                     T = length(seq(start, end))
                     t = seq(start, end)
            for (i in 2:T){x[i] = x[i-1] * ( 1 + r - r * x[i-1] / k - q * e[i-1])
                           e[i] = e[i-1] * ( 1 + eta * ( p * q * x[i-1] - c))}
                     return(x)}


```

