---
title: "Fishery Model"
date: "`r Sys.Date()`"
output: html_document
---

```{r pkg_ins, include = FALSE}

rm(list=ls())

# Check out knitr for knitr::read_chunk.
library(knitr)

# Name packages.
pkg <- c("readr",
         "knitr",
         "tidyverse",
         "gapminder",
         "sandwich",
         "broom",
         "stargazer",
         "cowplot",
         "kableExtra",
         "reshape2")

# Install packages.
#install.packages(pkg, verbose = FALSE, quiet = TRUE)
  
# Update packages.
#update.packages(pkg, verbose = FALSE, quiet = TRUE)

# Check out packages.
lapply(pkg, library, character.only = TRUE)

```

#####Objective: Step through optimal aggregate harvest in an open access fishery.
Swap out toy model for INAPESCA's age-structured model. Sort out selectivity and dam problems.

Toy Model (Conrad):

Stock

$X_{t+1} = X_t (1 + r - \frac{rX_t}{K} - qE_t)$

Yield-Effort

$Y_t = q X_t E_t$

Dynamic Effort

$E_{t+1} =  E_t ( 1 + \eta (p q X_t - c ))$

```{r placeholder_parameterization}

k = 50217

y_50 = 687
x0_50= 38820
x1_50= 38938

y_60 = 731
x0_60= 41829
x1_60= 41785

y_70 = 471
x0_70= 40617
x1_70= 40900

r_50 = (k * (y_50 - x0_50 + x1_50)) / (x0_50 * (k - x0_50))
r_60 = (k * (y_60 - x0_60 + x1_60)) / (x0_60 * (k - x0_60))
r_70 = (k * (y_70 - x0_70 + x1_70)) / (x0_70 * (k - x0_70))

r = (r_50 + r_60 + r_70) / 3

qe_50 = - r * x0_50 / k + r - x1_50 / k + 1
qe_60 = - r * x0_60 / k + r - x1_60 / k + 1
qe_70 = - r * x0_70 / k + r - x1_70 / k + 1

q = 0.001
n = 0.0001

e_50 = qe_50 / q
e_60 = qe_60 / q
e_70 = qe_70 / q

p = 10
c = p / 5

# Final parameterization:
y_10 = 752
x0_10= 18243
x1_10= 17756

r_10 = (k * (y_10 - x0_10 + x1_10)) / (x0_10 * (k - x0_10))

e_10 = ( - r_10 * x0_10 / k + r_10 - x1_10 / k + 1 ) / q

p_10 = 50
c_10 = p / 10

n_10 = 0.005

```


Variable  | Definition                  | Value
--------- | --------------------------- | ----------------------
*t*       | Timestep (Year)             |
*X*       | Stock (Tonnes)              |
*r*       | Growth (%)                  | `r r`
*K*       | Carrying Capacity (Tonnes)  | `r k`
*q*       | Catchability (Parameter)    | 
*E*       | Effort (Vessel Days)        |
$\eta$    | Adjustability (Parameter)   | `r n`
*p*       | Price (USD2018 / Ton)       | `r p`
*c*       | Cost (USD2018 / Vessel Day) | `r c`

#####1. Logistic Growth Demo

```{r stock_function}

# Workflow: build function, run function over some parameters, plot output.

# Growth / Stock, i.e. F(X)/X. NB: Not dynamic, just a demo of growth from different stocks.
fx_log = function(r, k, x){ fx = r * x * ( 1 - x / k )}

demo_x = seq(0, k, by = 1000)

demo_fx = fx_log(r, k, demo_x)

plot(demo_x, demo_fx)

# Growth / Time, w/o mortality.
x_log = function(r, k, x0, start, end){
                     v_n = as.numeric(vector(length=(end - start)))
                     v_n[1] = x0
                     t = length(seq(start, end))
            for (i in 2:t){v_n[i] = v_n[i - 1] + r * v_n[i - 1] * (1 - v_n[i - 1] / k)}
                     return(v_n)}


demo_x_log = x_log(r, k, x0_50, 1950, 1975)

t = seq(1950, 1975)

plot(t, demo_x_log)

```

```{r effort_function}

# Function for Effort at MSY:
#  Conrad pp87
demo_e = function(r, k, q, p, c){ e = ( r * ( p * q * k - c )) / ( p * q ^ 2 * k)}

# Effort / Price, Y = FX = MSY.
demo_p = seq(0.5 * p, 1.5 * p)

demo_e_p = demo_e(r, k, q, demo_p, c)

plot(demo_p, demo_e_p)

# Effort / Cost, Y = FX = MSY.
demo_c = seq(0.5 * c, 1.5 * c)

demo_e_c = demo_e(r, k, q, p, demo_c)

plot(demo_c, demo_e_c)

``` 

``` {r dynamic}
# Effort / Time.
# x_log modified to only return x for handy use in x_log_p - revert and make fresh function for x_log_p.
x_log = function(r, k, q, p, c, n, x0, e0, start, end){
                     x = as.numeric(vector(length = (end - start)))
                     x[1] = x0
                     e = as.numeric(vector(length = (end - start)))
                     e[1] = e_50
                     T = length(seq(start, end))
                     t = seq(start, end)
                     for (i in 2:T){x[i] = ifelse(x[i-1] * ( 1 + r - r * x[i-1] / k - q * e[i-1]) > 2,
                                                  x[i-1] * ( 1 + r - r * x[i-1] / k - q * e[i-1]),
                                                  2)
                                    e[i] = ifelse(e[i-1] * ( 1 + n * ( p * q * x[i-1] - c)) > 0,
                                                  e[i-1] * ( 1 + n * ( p * q * x[i-1] - c)),
                                                  0)}
                     #demo = tibble(t, x, e)
                     
                     return(x)}

# Model test for 1950 - 1975.
#demo_19 = x_log(r, k, q, p, c, n, x0_50, e_50, 1950, 1975)

#plot(demo_19$t, demo_19$x)
#plot(demo_19$t, demo_19$e)
#demo_19

# Model test for period of interest.
#demo_20 = x_log(r_10, k, n, p_10, c_10, 0.005, x0_10, e_10, 2010, 2020)

#plot(demo_20$t, demo_20$x)
#plot(demo_20$t, demo_20$e)
#demo_20

# Function for multiple runs stored in a matrix.
x_log_p = function(r, k, q, c, n, x0, e0, start, end, p_lwr, p_upr){
                      t = seq(start, end)
                      p = seq(p_lwr, p_upr)
                      mat_x_p = matrix(, nrow = length(t), ncol = length(p), dimnames = list(NULL, (paste("p_", p, sep = ""))))
                        for(j in 1:length(p)){mat_x_p[, j] = x_log(r, k, q, p_lwr + j, c, n, x0, e0, start, end)}
                      return(mat_x_p)}

# 1950 - 1975.
# Cough up a matrix and reformat it as a data frame with a time variable.
demo_19_p = x_log_p(r, k, q, c, n, x0_50, e_50, 1950, 1975, 5, 15) %>% 
  data.frame(.) #%>% 
  #mutate(., t = seq(0, 100)) #%>% 

# Fix this abomination.
demo_19_p_long = reshape2::melt(demo_19_p)

# This is part of the abomination.
demo_19_p_long = cbind(demo_19_p_long, rep(seq(1950, 1975), times = 11))
colnames(demo_19_p_long)[1:3] = c("p", "x", "t")

# Plot. Abomination stops here.
plot19 = ggplot(demo_x_log_p_long, aes(t, x, color = p, group = p)) + 
  geom_path() +
  theme(legend.position = "none")

# 2010 - 2020.
# Cough up a matrix and reformat it as a data frame with a time variable.
demo_20_p = x_log_p(r_10, k, q, c_10, n_10, x0_10, e_10, 2010, 2020, 45, 55) %>% 
  data.frame(.) #%>% 
  #mutate(., t = seq(0, 100)) #%>% 

# Fix this abomination.
demo_20_p_long = reshape2::melt(demo_20_p)

# This is part of the abomination.
demo_20_p_long = cbind(demo_20_p_long, rep(seq(2010, 2020), times = 11))
colnames(demo_20_p_long)[1:3] = c("p", "x", "t")

# Plot. Abomination stops here.
plot20 = ggplot(demo_20_p_long, aes(t, x, color = p, group = p)) + 
  geom_path() +
  theme(legend.position = "none")

# Plot by status. Thresholds are arbitrary. This gets you a flag effect, but not a path-dependency illustration.
#demo_x_log_p_long = mutate(demo_x_log_p_long, status = ifelse(x < 0.7, "bad", ifelse(x < 0.8, "meh", "good")))

#ggplot(demo_x_log_p_long, aes(t, x, group = p)) + 
  #geom_path() +
  #theme(legend.position = "none")

# Group by p, mutate status, ungroup?, plot with status by group.
#group_by
#mutate

#plot(demo_x_log_p$t, demo_x_log_p$p_150)

#ggplot(demo_x_log_p, aes(t, ))

```