---
title: "Fishery Model"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r pkg_ins, include = FALSE}

# rm(list=ls())

# Check out knitr for knitr::read_chunk.
library(knitr)

# Name packages.
pkg <- c("readr",
         "knitr",
         "tidyverse",
         "gapminder",
         "sandwich",
         "broom",
         "stargazer",
         "cowplot",
         "kableExtra",
         "reshape2")

# Install packages.
#install.packages(pkg, verbose = FALSE, quiet = TRUE)
  
# Update packages.
#update.packages(pkg, verbose = FALSE, quiet = TRUE)

# Check out packages.
lapply(pkg, library, character.only = TRUE)

```

#####Objective: Step through optimal aggregate harvest in an open access fishery.
Swap out toy model for INAPESCA's age-structured model. Sort out selectivity and dam problems.

Toy Model (Conrad):

Stock

$X_{t+1} = X_t (1 + r - r X_t / K - qE_t)$

Yield-Effort

$Y_t = q X_t E_t$

Dynamic Effort

$E_{t+1} =  E_t ( 1 + \eta (p q X_t - c ))$

Variable  | Definition
--------- | ---------------------------
*t*       | Timestep (Year)
*X*       | Stock (Tons)
*r*       | Growth (%)
*K*       | Carrying Capacity (Tons)
*q*       | Catchability (Parameter)
*E*       | Effort (Vessel Days)
$\eta$    | Adjustability (Parameter)
*p*       | Price (USD2018 / Ton)
*c*       | Cost (USD2018 / Vessel Day)

#####1. Logistic Growth Demo

```{r stock_function}

# Workflow: build function, run function over some parameters, plot output.

# Growth / Stock, i.e. F(X)/X. NB: Not dynamic, just a demo of growth from different stocks.
fx_log = function(r, k, x){ fx = r * x * ( 1 - x / k )}

demo_x = seq(0, 50)

demo_fx = fx_log(0.25, 50, demo_x)

plot(demo_x, demo_fx)

# Growth / Time, w/o mortality.
x_log = function(r, k, x0, start, end){
                     v_n = as.numeric(vector(length=(end - start)))
                     v_n[1] = x0
                     t = length(seq(start, end))
            for (i in 2:t){v_n[i] = v_n[i - 1] + r * v_n[i - 1] * (1 - v_n[i - 1] / k)}
                     return(v_n)}


demo_x_log = x_log(0.25, 50, 10, 2000, 2025)

t = seq(2000, 2025)

plot(t, demo_x_log)

```

```{r effort_function}

# Function for Effort at MSY:
#  Conrad pp87
demo_e = function(r, k, q, p, c, eta){ e = ( r * ( p * q * k - c )) / ( p * q ^ 2 * k)}

# Effort / Carrying Capacity.
demo_k = seq(0, 50)

demo_e_k = demo_e(0.25, demo_k, 0.05, 50, 1, 1)

plot(demo_k, demo_e_k)

# Effort / Price, Y = FX = MSY.
demo_p = seq(0, 50)

demo_e_p = demo_e(0.25, 50, 0.05, demo_p, 1, 1)

plot(demo_p, demo_e_p)

# Effort / Cost, Y = FX = MSY.
demo_c = seq(0, 50)

demo_e_c = demo_e(0.25, 50, 0.05, 50, demo_c, 1)

plot(demo_c, demo_e_c)

``` 

``` {r dynamic}
# Effort / Time.
# x_log modified to only return x for handy use in x_log_p - revert and make fresh function for x_log_p.
x_log = function(r, k, q, p, c, eta, x0, e0, start, end){
                     x = as.numeric(vector(length = (end - start)))
                     x[1] = x0
                     e = as.numeric(vector(length = (end - start)))
                     e[1] = e0
                     T = length(seq(start, end))
                     t = seq(start, end)
            for (i in 2:T){x[i] = x[i-1] * ( 1 + r - r * x[i-1] / k - q * e[i-1])
                           e[i] = e[i-1] * ( 1 + eta * ( p * q * x[i-1] - c))}
                     return(x)}


#demo_x_log = x_log(0.1, 1, 0.01, 200, 1, 0.3, 0.50, 1.00, 0, 100)

#plot(demo_x_log$x, demo_x_log$e)

#plot(demo_x_log$t, demo_x_log$x)

# Function for multiple runs stored in a matrix.
x_log_p = function(r, k, q, c, eta, x0, e0, start, end, p_lwr, p_upr){
                      t = seq(start, end)
                      p = seq(p_lwr, p_upr)
                      mat_x_p = matrix(, nrow = length(t), ncol = length(p), dimnames = list(NULL, (paste("p_",p_lwr:p_upr, sep = ""))))
                        for(j in 1:length(p)){mat_x_p[, j] = x_log(r, k, q, (j+p_lwr-1), c, eta, x0, e0, start, end)}
                      return(mat_x_p)}

# Cough up a matrix and reformat it as a data frame with a time variable.
demo_x_log_p = x_log_p(0.1, 1, 0.01, 1, 0.3, 0.50, 1.00, 0, 250, 50, 150) %>% 
  data.frame(.) #%>% 
  #mutate(., t = seq(0, 100)) #%>% 

# Fix this abomination.
demo_x_log_p_long = reshape2::melt(demo_x_log_p)

# This is part of the abomination.
demo_x_log_p_long = cbind(demo_x_log_p_long, rep(seq(0, 250), times = 101))
colnames(demo_x_log_p_long)[1:3] = c("p", "x", "t")

# Plot. Abomination stops here.
fish = ggplot(demo_x_log_p_long, aes(t, x, color = p, group = p)) + 
  geom_path() +
  theme(legend.position = "none")

# Plot by status. Thresholds are arbitrary. This gets you a flag effect, but not a path-dependency illustration.
#demo_x_log_p_long = mutate(demo_x_log_p_long, status = ifelse(x < 0.7, "bad", ifelse(x < 0.8, "meh", "good")))

ggplot(demo_x_log_p_long, aes(t, x, group = p)) + 
  geom_path() +
  theme(legend.position = "none")

# Group by p, mutate status, ungroup?, plot with status by group.
#group_by
#mutate

#plot(demo_x_log_p$t, demo_x_log_p$p_150)

#ggplot(demo_x_log_p, aes(t, ))

```