---
title: "Market Model"
date: "`r Sys.Date()`"
output: html_document
---

#####Objective: Visualize database of prices for swim bladder at first and final sale.

1. When was data collected?
2. Where was data collected?
3. On what species was data collected, and in what volume?
4. How's the price distribution?
4.1. How's the price distribution over swim bladder weight?
5. How's the price distribution over time for totoaba?
6. What does the INAPESCA harvest estimate indicate about export volume?
7. What do price distributions and estimated export volumes by year suggest about the demand function?

Bonus: is stockpiling apparent or plausible?

```{r pkg_ins, include = FALSE}

rm(list=ls())

# Check out knitr for knitr::read_chunk.
library(knitr)

# Name packages.
pkg <- c("readr",
         "knitr",
         "tidyverse",
         "gapminder",
         "sandwich",
         "broom",
         "stargazer",
         "pander",
         "cowplot",
         "kableExtra")

# Install packages.
install.packages(pkg, verbose = FALSE, quiet = TRUE)

  
# Update packages.
#update.packages(pkg, verbose = FALSE, quiet = TRUE)

# Check out packages.
lapply(pkg, library, character.only = TRUE)

```

#####1. Reading Data
Data has sources, uses, and shortcomings.

```{r data, message = FALSE}

# Read data.
dat_other = read_csv('GP_OtherBuchePrices.csv')
dat_tma   = read_csv('GP_TotoabaBuchePrices.csv')

```

#####2. Cleaning Data
Everyone loves cleaner data.

```{r clean}

# Drop, rename, and rearrange variables for a full join.
dat_tma = dat_tma %>%
  select(-Month, 
         -`Price (USD/kg)`, 
         -`Price (per lb.)`, 
         -`Price (per buche local)`, 
         -`Price (per buche Asia)`, 
         -`Condition (Inferred)`) %>%
  rename(year = Year,
         price_gram = "Price (USD/g)", 
         "price_total" = "Total Value (USD)",
         "kg_buche" = "Mass/Buche (kg)",
         "kg_total" = "Mass (kg.)",
         "count_buche" = "Number of buche",
         "condition_infer" = "Condition (Inferred)_1",
         "condition" = Condition,
         "place" = Country, 
         "source" = Source) %>% 
  mutate(sp_sci = "Totoaba macdonaldi") %>% 
  mutate(sp_com = "Totoaba") %>% 
  tbl_df()

dat_other = dat_other %>%
  select(., 
         -Month, 
         #-`Species (Scientific)`, 
         #-`Species (Common)`, 
         -`Price / lb (USD)`, 
         -`Price / Buche (USD)`, 
         -`Total Volume (lbs)`,
         -`Location (City/Other)`, 
         -Notes) %>% 
  rename(.,
         "year" = Year,
         "price_gram" = "Price / kg (USD)",
         "price_total" = "Total Value (USD)",
         "kg_total" = "Total Volume (kg)",
         "count_buche" = "Buche Count",
         "condition_infer" = Condition,
         "condition" = Condition,
         "place" = "Location (Country)", 
         "source" = Source,
         "sp_sci" = `Species (Scientific)`,
         "sp_com" = `Species (Common)`) %>%
  mutate(., condition_infer = condition) %>%
  mutate(., price_gram = price_gram * 0.001) %>%
  mutate(., count_buche = 1) %>% 
  tbl_df(.)

# Fix default types.
dat_other$price_total = as.double(dat_other$price_total)
dat_other$kg_total = as.double(dat_other$kg_total)

# Full join data for totoaba and other species.
dat = full_join(dat_tma, dat_other)

# Distinguish totoaba from other species by a dummy.
dat = mutate(dat, tma = ifelse(sp_com == "Totoaba", 1, 0))

```

#####3. Adjusting Prices for Inflation
Inflation is neat. Thanks, sources!

```{r real}

# Adjust data for inflation.
# Inflation estimates by the Bureau of Labor Statistics, bls.gov/bls/inflation.htm and bls.gov/data/inflation_calculator.htm
# Accessed 11/3/2018. All inflation adjustments queried for January 20** against January 2018.

# Create vectors for years and inflation adjustment by year.
year = c(2000:2018)
infl = c(1.47, 1.42, 1.40, 1.36, 1.34, 1.30, 1.25, 1.22, 1.17, 1.17, 1.14, 1.13, 1.09, 1.08, 1.06, 1.06, 1.05, 1.02, 1.00)

# Tibble.
dat_infl = tibble(year, infl)

# Smoosh inflation adjustents up on the database.
dat = left_join(dat, dat_infl, by = "year")

# Mutate adjusted prices out of nominal prices and inflation adjustments.
dat = dat %>% 
  mutate(., p_g_r = price_gram * infl) %>% 
  mutate(., p_t_r = price_total * infl)

```

#####4. Adding Harvest Estimates
Totoaba is delicious, but sadly often goes uneaten. Thanks, INAPESCA!

```{r q}

# Fix arbitrary value for 2018.

# Join INAPESCA estimate of totoaba harvest in metric tonnes to database.
year = c(2000:2018)
y_biomass = c(462, 485, 509, 535, 562, 590, 619, 650, 682, 717, 752, 790, 869, 956, 1051, 1156, 1272, 1400, 1550)

# Convert estimate of biomass to wet buche from 2.5% estimate (MC Pers. Comm, Ogunja et al. 1988).
y_wet = y_biomass*0.025

# Convert wet buche to dry from 40% estimate (Centre for Food Technology 1994, Food Safety Alliance 2018.
y_dry = y_wet*0.400

# Tibble.
dat_q = tibble(year, y_dry)

# Smoosh estimated export volume of dry buche up on the database.
dat = left_join(dat, dat_q, by = "year")

```

#####5. Visualizations
All that really matters is graphs.

```{r figs, echo = FALSE, width = 6.5, height = 4.5, dpi = 300, eval = FALSE}

# break this up by group of figures ; add captions for each group, or for each as necessary

# frequency of mass by bins, simple
# fix breaks
#ggplot(dat, aes(p_g_r, fill = factor(tma))) +
#  geom_histogram(binwidth=10, position="identity") +
#  theme_classic()

# price by year, jitter, totoaba and other species
tmaplus = ggplot(dat, aes(year, price_gram)) + 
  geom_jitter(aes(shape = factor(place), colour = factor(tma))) + 
  labs(x = "Year", y = "Nominal USD / Gram", title = "Observed Prices for Swim Bladder, 2000 - 2018") +
  scale_x_continuous(breaks = c(2005:2018), limits = c(2005,2018)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        legend.text = element_text(size = 8),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        legend.title = element_text(size = 9),
        plot.title = element_text(size = 10))

# price by year, jitter, totoaba only
tma = ggplot(filter(dat, tma == 1), aes(year, price_gram)) + 
  geom_jitter(width = 0.15, aes(shape = factor(place), colour = factor(condition_infer))) + 
  labs(x = "Year", y = "Nominal USD / Gram", title = "Observed Prices for Totoaba Swim Bladder", shape="Location", colour="Condition") +
  scale_x_continuous(breaks = c(2014:2018), limits = c(2014,2018)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        legend.text = element_text(size = 8),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        legend.title = element_text(size = 9),
        plot.title = element_text(size = 10))

# usd2018/gram scatter 
pgr_grams = ggplot(filter(dat, tma == 1), aes(kg_buche*1000, p_g_r)) + 
  geom_point() + 
  labs(x = "Grams", y = "USD2018 / Gram") +
  scale_x_continuous(breaks = seq(0, 2500, by = 500), limits = c(0, 2500)) +
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 100)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        legend.text = element_text(size = 8),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        legend.title = element_text(size = 9),
        plot.title = element_text(size = 10))

# usd2018/place (discrete, US, MX, HK, CN) jitter
pgr_place = ggplot(filter(dat, tma == 1 & place != "United States"), aes(place, p_g_r)) +
  geom_jitter(width = 0.25) +
  labs(x = "", y = "USD2018 / Gram") +
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 100)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        legend.text = element_text(size = 8),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        legend.title = element_text(size = 9),
        plot.title = element_text(size = 10))


# usd2018/condition (dry, wet) jitter
pgr_condition = ggplot(filter(dat, tma == 1), aes(condition_infer, p_g_r)) +
  geom_jitter(width = 0.25) +
  labs(x = "", y = "USD2018 / Gram") +
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 100)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        legend.text = element_text(size = 8),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        legend.title = element_text(size = 9),
        plot.title = element_text(size = 10))


# usd2018/q (estimated from INAPESCA 2018) jitter
pgr_quantity = ggplot(filter(dat, tma == 1 & year < 2018), aes(y_dry, p_g_r)) +
  geom_point() +
  labs(x = "Estimated Annual Post-Processing Totoaba Maw Production (Tonnes)", y = "USD2018 / Gram") +
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 100)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        legend.text = element_text(size = 8),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        legend.title = element_text(size = 9),
        plot.title = element_text(size = 10))

# grid
# fix grid please
pgr_all = plot_grid(pgr_place, pgr_condition, pgr_grams, pgr_quantity)
ggsave("pgr_all.pdf", dpi = 300, pgr_all)

# box/whiskers for prices by species w/ labels for n 
# jitter for prices by species

# bar estimated export volume by year
# + 3d option for same w/ weight distribution

# !!!
# bar estimated export value by year
# + 3d option for same w/ weight distribution
# !!!


```

```{r show, eval = FALSE}

# Display figures.
tma
tmaplus
pgr_grams
pgr_place
pgr_condition
pgr_quantity
pgr_all

```

```{r save, eval = FALSE}

# Save figures.

#ggsave("filename.filetype", ggobject)

```

#####6. Multiple Regression Analysis
OLS suits the question for reasons. Necessary assumptions are several.

```{r spec}

# Totoaba only.

# Assign specifications for linear models of price.
#  Get a cleaner database.
    minidat = select(dat, 
                     year, 
                     p_g_r,
                     y_dry,
                     kg_buche, 
                     condition_infer, 
                     place, 
                     sp_com)
    
    minidat = rename(minidat,
                    "year" = year,
                    "p" = p_g_r,
                    "q" = y_dry,
                    "kg" = kg_buche,
                    "cond" = condition_infer,
                    "place" = place,
                    "spp" = sp_com)
    
    minidat = filter(minidat, !is.na(p))

    minidat = mutate(minidat, g = kg*1000)
    
    minidat = mutate(minidat, bicond = ifelse(cond == "Wet", 0, 1))
    
    tinydat = filter(minidat, spp == "Totoaba" & bicond == 1)
    
    #tinydat = select(filter(minidat, spp == "Totoaba"),
                     #"Price (USD2018)" = p,
                     #"Grams / Unit" = g,
                     #"Quantity Supplied (Tonnes)" = q, 
                     #"Processing" = bicond)
    tinydat = na.omit(tinydat)

    # Intuition: for any maw, price follows supply, weight, and processing.
#lm = lm((`Price (USD2018)`) ~ (`Quantity Supplied (Tonnes)`) + (`Grams / Unit`) + (`Processing`), data = tinydat)
#lm = lm(p ~ q + g, data = tinydat)
#lmlog = lm(log(p) ~ log(q) + g, data = tinydat)
nlm = nls(p ~ q * a + (g ^ b) + c, data = tinydat, start = c(a = -5.00, b = 2.00, c = 20))

```

```{r star, results='asis'}

# Display model results.
#stargazer(lm, type = "latex", digits = 2)

```

```{r nlm_tidy}

nlm_tidy = tidy(nlm)
tinydat_aug = augment(nlm, tinydat)

```

```{r nlm_plots}

# Price against grams maw.
plot_nlm_g =
  ggplot(tinydat_aug) +
  geom_point(aes(g, p), colour = "gray50") +
  geom_segment(aes(x = g, y = p, xend = g, yend = .fitted), colour = "gray50") +
  geom_point(aes(g, .fitted), colour = "firebrick") +
  labs(x = "Grams of Dry Maw", y = "USD2018 / Gram") +
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 100), expand = c(0, 0)) +
  #ggtitle("Observed and Estimated Prices for Totoaba Maw by Maw Weight") +
  theme(axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        legend.text = element_text(size = 8),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        legend.title = element_text(size = 9)) +#,
        #plot.title = element_text(size = 9)) +
  theme_classic()

# Price against tonnes maw.
plot_nlm_q = 
  ggplot(tinydat_aug) +
  geom_boxplot(aes(as.factor(q), .fitted), colour = "firebrick") +
  geom_jitter(aes(as.factor(q), p), colour = "gray50") +
  labs(x = "Tonnes of Dry Maw at Market", y = "USD2018 / Gram") +
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 100), expand = c(0, 0)) +
  #ggtitle("Observed and Estimated Prices for Totoaba Maw by Maw Production") +
  theme(axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        legend.text = element_text(size = 8),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        legend.title = element_text(size = 9)) +#,
        #plot.title = element_text(size = 9)) +
  theme_classic()

# Price against quantity, with some prerequisite math first.
pintl = as.numeric(nlm_tidy[3, 2])
qintl = - as.numeric(nlm_tidy[3, 2]) / as.numeric(nlm_tidy[1, 2])
pinth = as.numeric(nlm_tidy[3, 2]) + 1000^as.numeric(nlm_tidy[2, 2])
qinth = - (as.numeric(nlm_tidy[3, 2]) + 1000^as.numeric(nlm_tidy[2, 2])) / as.numeric(nlm_tidy[1, 2])
pintll= pintl + as.numeric(nlm_tidy[1, 2]) * qinth
pinthm= pinth + as.numeric(nlm_tidy[1, 2]) * qintl

# Throw intercepts into a data frame.
invd  = data.frame(c(0, qintl, qinth), c(pintl, 0, pintll), c(pinth, pinthm,0)) 
colnames(invd) = c("q", "pl", "ph")

plot_invd =
ggplot() +
  geom_ribbon(data = invd, aes(q, ymin = pl, ymax = ph), alpha = 0.5, colour = "firebrick", fill = "firebrick") +
  geom_point(data = tinydat_aug, aes(q, p), colour = "gray50") +
  coord_cartesian(xlim = c(0, qinth), ylim = c(0, pinth), expand = FALSE) +
  labs(x = "Tonnes of Dry Maw at Market", y = "USD2018 / Gram") +
  #ggtitle("Observed and Estimated Prices for Totoaba Maw by Maw Production") +
  theme(axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        legend.text = element_text(size = 8),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        legend.title = element_text(size = 9)) +#,
        #plot.title = element_text(size = 9)) +
  theme_classic()

# Kablify the model.
nlm_tidy$term = c("Supply (Tonnes)", "Weight (Grams)", "Choke Price")
colnames(nlm_tidy) = c("", "Coef.", "SE", "t", "p")
kable(nlm_tidy, format = "html", caption = "Inverse Demand Specification", digits = 3) %>% 
  kable_styling("striped", full_width = F) #%>
  #cat(file = "kab_nlm.html"

```

```{r plotsave}

ggsave("plot_nlm_g.png", plot_nlm_g, width = 6.5, height = 4.5, dpi = 300)
ggsave("plot_nlm_q.png", plot_nlm_q, width = 6.5, height = 4.5, dpi = 300)
ggsave("plot_invd.png", plot_invd, width = 6.5, height = 4.5, dpi = 300)

```

